### 2025-03-24 paper-reviews/papers-2025.tex
Add MLPerf Training paper

    The article presents LoRA (Low-Rank Adaptation) technique for large language models. The technique is aimed to speedup fine-tuning and inference of the fine-tuned model. Traditionally, fine-tuning is used to update weights of a model pre-trained on a large set of generic data in order to specialize the model to handle a specific task. Basically it is a retraining of a generic model on a dataset specific for a desired task. With large language model it poses an obvious issue --- the fine-tuned model has the same number of parameters as the original model which makes the retraining task expensive and long. The main idea of LoRA is to freeze the pre-trained model weights and inject additional trainable rank decomposition matrices into the model in order to greatly reduce the number of trainable parameters. This approach allows easy switch of the model in production environment --- only the smaller additional matrices need to be switched. It is also possible to merge the trainable matrices into the original pre-trained model weights to avoid introducing extra latency during inference. The LoRA matrices consist of down projection from the original dimension to a small LoRA rank (the authors showed that even rank of two can be efficient) and up projection back to the original dimension. The high level idea is that the LoRA rank will record information specific for a desired task. The paper shows that it is preferable to adopt more weight matrices than to adopt a single weight matrix with a larger rank.
\end{itemize}

>>>>

    The article presents LoRA (Low-Rank Adaptation) technique for large language models. The technique is aimed to speedup fine-tuning and inference of the fine-tuned model. Traditionally, fine-tuning is used to update weights of a model pre-trained on a large set of generic data in order to specialize the model to handle a specific task. Basically it is a retraining of a generic model on a dataset specific for a desired task. With large language model it poses an obvious issue --- the fine-tuned model has the same number of parameters as the original model which makes the retraining task expensive and long. The main idea of LoRA is to freeze the pre-trained model weights and inject additional trainable rank decomposition matrices into the model in order to greatly reduce the number of trainable parameters. This approach allows easy switch of the model in production environment --- only the smaller additional matrices need to be switched. It is also possible to merge the trainable matrices into the original pre-trained model weights to avoid introducing extra latency during inference. The LoRA matrices consist of down projection from the original dimension to a small LoRA rank (the authors showed that even rank of two can be efficient) and up projection back to the original dimension. The high level idea is that the LoRA rank will record information specific for a desired task. The paper shows that it is preferable to adopt more weight matrices than to adopt a single weight matrix with a larger rank.

    \item \cite{Mattson:MLPerfTraining:2020}:

    The paper present MLPerf training benchmark and describes challenges that are rather unique for machine learning workloads: stochastic nature of the training task; necessity to train to the completion to be able to compare model quality. For example, lower data precision from FP32 to BF16 will definitely improve training throughput but it may require a lot more iterations to complete the training task (achieve similar model quality). The benchmark includes a set of model architectures aimed to solve the most common machine learning tasks including image classification, object detection, translation (both transformer and RNN), etc.
\end{itemize}
